\chapter{Data Selection and Preprocessing}
\section{Data Selection}
The saying "garbage in garbage out" succinctly states the importance of selecting data for machine learning models.
It does not matter how powerful a model is if the data selected is poor or inappropriate.
Selecting data is a key step to building effective machine-learning models.
Thankfully, there are plenty of large open-source data sets available online, yet picking an appropriate set may still present a challenge.
The dataset that will be used for this project is the United Kingdom subset of "World Development Indicators"\cite{WBI}.
My reason for selecting this set is due to its large number of metrics, reliable provider, and the fact that it is open-source.
The dataset is classified as public under the access to information classification policy. 
The World Bank is known for reliable and accurate data which should avoid issues of bias, insufficient data, or poor quality.
The original UK dataset contains over 1400 metrics with data running from 1960-2022 including 2 metrics for inflation (CPI and GDP deflator (the rate of price change in the economy as a whole)).
However, due to the all-encompassing nature of the dataset, it will need to be cleaned and many columns will need to be removed to improve the set's relevance.

\section{Data Preprocessing}
Often, datasets have several outstanding issues or properties that make them imperfect for use in a machine-learning model.
Data preprocessing is the process of making changes to and cleaning a dataset before using it in a model.
